Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-11 eswc-2012/phdsymp.tex
use little space
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@65 43ef1190-90fd-4dd7-a769-d0121f02b80e

This problem has already received some attention, \cite{5337556}
addressed this problem by making it possible to exchange histograms,
but I suspect this will prove to become untenable as the number of
histograms to be computed and the number of bins in each histogram to
represent highly heterogenous data would be very high. This would also
cause the amount of statistical data to be exchanged between endpoints
to be very high.

>>>>

This problem has already received some attention, \cite{5337556}
addressed this problem by making it possible to exchange histograms
and other data, and \cite{Harth:2010:DSO:1772690.1772733} introduced
QTrees. I suspect these approaches will suffer from either involving
too much statistical data or if constraining the data size, leaving
too much out. The problem becomes how to digest the most useful
statistics in as little as possible space.
